Verifying Demonstrations

### 2018-08-26 paper/adversary-model.tex
Adds that adversary must link IOIs
We must still specify what this linking means (see #127).
Fixes typo in adversary model

\begin{definition}[Base identity--cause adversary]%
  \label{base-identity-cause-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learn only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
  \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), where \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{definition}

@@

The players are still the same, but now the adversary controls other players: 
in particular, the adversary controls the protester \(P\) and the storage 
\(S\).

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W, l)\) and the time it took place, 
  \(t_{P,W}\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(S\).
\end{definition}

>>>>

\begin{definition}[Base identity--cause adversary]%
  \label{base-identity-cause-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learn only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
  \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), where \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
  The adversary wins if he can link \(\cid\) and \(P\).
\end{definition}

@@

The players are still the same, but now the adversary controls other players: 
in particular, the adversary controls only the storage \(S\).

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W, l)\) and the time it took place, 
  \(t_{P,W}\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(S\).
  The adversary wins if he can link \(W\) and \(l\).
\end{definition}
